Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-11-07 papers/thesis-kirstie/thesis.tex
edits

centered at each lattice site.

@@

$\vec{r'}$ according to a Gaussian distribution. 

@@

Only lengths for $\vec{r'}$ that are within an inclusion radius

@@

Gaussian centered about a lattice site is given by

@@

\begin{equation}{n_i(\vec{r})= \int_{r'}{(1-f_v)n(\vec{r'})w_i(|\vec{r}-\vec{r}'|)} {d}\vec{r}'}\end{equation} 

@@

\begin{equation}{n_i(\vec{r})= \sum_{r'}{(1-f_v)n(\vec{r'})w_i(|\vec{r}-\vec{r}'|)dV}}\end{equation} 

@@

\begin{equation}{n_i(\vec{r})= \sum_{NumPoints}(1-f_v)P_{r'}w_i(|\vec{r}-\vec{r}'|)}\end{equation} 
where NumPoints is the number of vectors $\vec{r'}$ randomly generated, 

@@

and $n(\vec r')$

@@

from the Gaussians around each lattice point which are then added together 
to get the final value of the weighted density. 
The result can be made more accurate by increasing NumPoints which is the 
number of vectors randomly generated.

 \begin{figure}[h!]
    \centering
    %\includegraphics[height=6cm]{GaussandW2_actual.png}
    \includegraphics[height=7cm]{weightandGuass1.pdf}
    %\caption{A Gaussian centered at $\vec{R}$ is shown in blue, and a cross-sectional 
    %view of $w_2$ centered at $\vec{r}'$ is shown in purple.} 
    \caption{A Gaussian distribution about a lattice site is shown in blue, and a cross-sectional 
    view of $w_2$ centered at $\vec{r}'$ is shown in purple.} 
    %Here, the weight function 
    %is evaluated at $\vec{r}-\vec{r}'$ where $\vec{r}'=\vec{R}+\vec{dr}$ and $\vec{dr}$ 
    %is generated randomly according to a Gaussian distribution.} 
  \label{fig:GaussandW2_actual}
  \end{figure}

 \begin{figure}[h!]
    \centering
    %\includegraphics[height=6cm]{GaussandW2_thinkas.png}
    \includegraphics[height=7cm]{weightandGuass2.pdf}
    \caption{An alternative way of viewing Figure~\ref{fig:GaussandW2_actual} where 
    the weight function, shown by the purple dashed lines, is centered at $\vec{r}$,  
    and fixed in place as $\vec r'$
    %as $\vec{dr}=\vec{r}'-\vec{R}$ 
    varies randomly with a probability according to a Gaussian distribution.} 
  \label{fig:GaussandW2_thinkas}
  \end{figure}

%Monte-Carlo integration is employed to more efficiently 
%compute the weighted densities used to calculate the excess free energy which is then 
%added to the ideal free energy (computed analytically) to get the total free energy 
%which is minimized.

%-------Antithetic-------------------
In order to further reduce the error 
in the average, antithetic variates are used. Rather than computing an average 
of a set of random points, each random point in the set is paired with a 
point along the same line as the first point, but opposite in direction, 
as shown in Figure \ref{fig:AntitheticVariate}. This reduces first order 
error in the average by filtering out an erroneous offset of values along 
the line connecting the two points by averaging the two results, one of 
which may be erroneously higher than it should be while the other is 
erronesously lower than it should be.

 \begin{figure}[h!]
    \centering
    \includegraphics[height=4cm]{AntitheticVariate.png}
    \caption{Antithetic variates reduce first order error in an average. 
    Each point in the average is paired with another point from along 
    the same line as the first, and at an equal, but opposite distance.}
    \label{fig:AntitheticVariate}
  \end{figure} 
%Incorporating antithetic variates $-\vec{dr}$ for every $\vec{dr}$ equation ?? becomes:
%\begin{displaymath}{n_i(\vec{r}_k, \vec{R}_j)=\sum_{NumPoints}\frac{1}{2}\frac{(1-f_v)\left[w_i(|\vec{r}-\vec{R_j}-\vec{dr}|) +w_i(|\vec{r}-\vec{R_j}+\vec{dr}|)\right]}{NumPoints}}\end{displaymath}   
%The process is repeated for all the other $\vec{R}_j$'s to get the total 
%weighted densities at vector $\vec{r}_k$ due to all the Gaussians. 
%\begin{displaymath}{n_i(\vec{r}_k)=\sum_j{n_i(\vec{r}_k, \vec{R}_j)}}\end{displaymath}
%Then the entire process repeated for each vector $\vec{r}_k$ to get the 
%total weighted densities $n_i(\vec{r})$ as a function of the position $\vec{r}$.

The standard error of the mean (SEM) is given in general by
\begin{equation}{SD_{mean}=\frac{SD}{\sqrt{N}}}\end{equation} 
%which gives a measure of the error in $n_3=\overline{w}_3$:
To compute the error, the standard deviation of weight function $w_3$ is used 
\begin{equation}SD=\sqrt{\overline{w_3^2}-(\overline{w}_3)^2}\end{equation} 
\begin{equation}{Error=\sqrt{\frac{\overline{w_3^2}-(\overline{w}_3)^2}{\text{NumPoints}}}}\end{equation} 
NumPoints, the number of vectors randomly generated, is increased until
\begin{equation}{Error<\frac{|1-n_3|}{4}}\end{equation}
where the maximum value that $n_3$ (which equals $\overline{w}_3$) can have without error is 1.

>>>>

centered at lattice sites specified by position vectors $\vec R$. 
%where j indicates the jth lattice site.

@@

$\vec r' -\vec R$ according to a Gaussian distribution. 

@@

Only lengths for $\vec r'- \vec R$ that are within an inclusion radius

@@

Gaussian centered at the jth lattice site located at $\vec R_j$ is given by

@@

\begin{equation}{n_i(\vec r)= \int_{r'}{(1-f_v)n(\vec r' - \vec R_j)w_i(|\vec{r}-\vec{r}'|)} {d}\vec{r}'}\end{equation} 

@@

\begin{equation}{n_i(\vec r)= \sum_{r'}{(1-f_v)n(\vec r' -\vec R_j)w_i(|\vec{r}-\vec{r}'|)dV}}\end{equation} 

@@

\begin{equation}{n_i(\vec r)= \sum_{NumPoints}(1-f_v)P_{r'}w_i(|\vec{r}-\vec{r}'|)}\end{equation} 
NumPoints is the number of vectors $\vec r' - \vec R_j$ randomly generated about the jth lattice site, 

@@

and $n(\vec r' - \vec R_j)$

@@

$n_i(\vec r)$ from the Guassians around each lattice point which begin to 
merge together as the width of the Guassians increases.
All the contributions are then added together 
to get the final value of the weighted density at some point $\vec r$.

The result can be made more accurate by increasing NumPoints (the 
number of vectors randomly generated), and by using antithetic variates.
%
 \begin{figure}[h!]
    \centering
    %\includegraphics[height=6cm]{GaussandW2_actual.png}
    \includegraphics[height=7cm]{weightandGuass1.pdf}
    %\caption{A Gaussian centered at $\vec{R}$ is shown in blue, and a cross-sectional 
    %view of $w_2$ centered at $\vec{r}'$ is shown in purple.} 
    \caption{A Gaussian distribution about a lattice site located at 
    $\vec R$ is shown in blue, and a cross-sectional 
    view of $w_2$ centered at $\vec{r}'$ is shown in purple.} 
    %Here, the weight function 
    %is evaluated at $\vec{r}-\vec{r}'$ where $\vec{r}'=\vec{R}+\vec{dr}$ and $\vec{dr}$ 
    %is generated randomly according to a Gaussian distribution.} 
  \label{fig:GaussandW2_actual}
  \end{figure} 
%
 \begin{figure}[h!]
    \centering
    %\includegraphics[height=6cm]{GaussandW2_thinkas.png}
    \includegraphics[height=7cm]{weightandGuass2.pdf}
    \caption{An alternative way of viewing Figure~\ref{fig:GaussandW2_actual} where 
    the weight function, shown by the purple dashed lines, is centered at $\vec{r}$,  
    and fixed in place as $\vec r' - \vec R$
    %as $\vec{dr}=\vec{r}'-\vec{R}$ 
    varies randomly with a probability according to a Gaussian distribution.} 
  \label{fig:GaussandW2_thinkas}
  \end{figure} 
%
%Monte-Carlo integration is employed to more efficiently 
%compute the weighted densities used to calculate the excess free energy which is then 
%added to the ideal free energy (computed analytically) to get the total free energy 
%which is minimized. 
%
%-------Antithetic-------------------
%To further reduce the error in the average, antithetic variates are used. 
%Rather than computing an average of a set of random points, 
%antithetic variates can be used to reduce error. 
To use antithetic variates,
each randomly generated  vector is paired with a 
vector of equal magnitude, but opposite in direction. 
%as shown in Figure \ref{fig:AntitheticVariate}. 
%The quantity that is a function of the randomly generated vector
%now has two values that can be averaged to get a more accurate value. 
First order error is reduced
%in the quantity that is a function of the randomly generated vector
%average by filtering out an erroneous offset of values 
%along the line connecting the two points 
by averaging the two results, one of 
which may be erroneously higher than it should be while the other is 
erronesously lower than it should be.

 \begin{figure}[h!]
    \centering
    %\includegraphics[height=4cm]{AntitheticVariate.png}
    %\caption{Antithetic variates reduce first order error in an average. 
    %Each point in the average is paired with another point from along 
    %the same line as the first, and at an equal, but opposite distance.}
    \label{fig:AntitheticVariate}
  \end{figure} 
%Incorporating antithetic variates $-\vec{dr}$ for every $\vec{dr}$ equation ?? becomes:
%\begin{displaymath}{n_i(\vec{r}_k, \vec{R}_j)=\sum_{NumPoints}\frac{1}{2}\frac{(1-f_v)\left[w_i(|\vec{r}-\vec{R_j}-\vec{dr}|) +w_i(|\vec{r}-\vec{R_j}+\vec{dr}|)\right]}{NumPoints}}\end{displaymath}   
%The process is repeated for all the other $\vec{R}_j$'s to get the total 
%weighted densities at vector $\vec{r}_k$ due to all the Gaussians. 
%\begin{displaymath}{n_i(\vec{r}_k)=\sum_j{n_i(\vec{r}_k, \vec{R}_j)}}\end{displaymath}
%Then the entire process repeated for each vector $\vec{r}_k$ to get the 
%total weighted densities $n_i(\vec{r})$ as a function of the position $\vec{r}$.

The standard error of the mean (SEM) is given in general by
\begin{equation}{SD_{mean}=\frac{SD}{\sqrt{N}}}\end{equation} 
%which gives a measure of the error in $n_3=\overline{w}_3$:
To compute the error, the standard deviation of weight function $w_3$ is used 
\begin{equation}SD=\sqrt{\overline{w_3^2}-(\overline{w}_3)^2}\end{equation} 
\begin{equation}{Error=\sqrt{\frac{\overline{w_3^2}-(\overline{w}_3)^2}{\text{NumPoints}}}}\end{equation} 
NumPoints, the number of vectors randomly generated, is increased until
\begin{equation}{Error<\frac{|1-n_3|}{4}}\end{equation}
where the maximum value that the weighted density $n_3$ 
%(which equals $\overline{w}_3$) 
can properly have is 1.
